Extended Data

### 2022-03-11 doc/manuscript/Dow_manuscript_Nature.Rmd
discussion

<!--the dominant effect of temperature on ANPP_woody is a negative effect of gs temperature-->

>>>>

<!--the dominant effect of temperature on ANPP_woody is a negative effect of gs temperature-->
Irregardless of the influence of spring temperatures on C cycling within the ecosystem, our results make clear that the dominant effect of temperatures on tree growth occur not in the spring, but during the peak growing season. 
Indeed, the timing of peak growth in June and July (`r EDT_phenology_parameters`, `r EDF_growth_curves_all`) coincides with the timing of the greatest sensitivity of annual growth to $T_{max}$ (Fig. `r tree_rings`, `r EDT_tree_ring_summary`).
This finding is consistent with numerous tree-ring studies demonstrating strong sensitivity of growth to drought stress[@refs] or high temperatures[@refs] during the peak growing season.
